\begin{frame}{Other corollaries}

    \begin{itemize}
        \item Lower bounds for monotone circuit (\alert{general technique}).
        \item Monotone function in $\NC^2$ that cannot be computed if polysize monotone ckt.
        \item Connection between: Proof Complexity, Circuit Complexity, TFNP.
        \item Separation between Cutting Planes and Nusstellensatz proof system.
        \item etc.
    \end{itemize}
\end{frame}


\begin{frame}{My results in proof complexity}
        
    \begin{itemize}
        \item Lower bounds for (Semi)Algebraic proofs over $\pm 1$ variables.
            \begin{itemize}
                \item Open problem: Impagliazzo, Pitassi and Mouli 2019.
            \end{itemize}
        \pause
        \item Hardness of inversion of Pseudorandom generators in Resolution.
            \begin{itemize}
                \item Open problem:
                    \begin{itemize}
                        \item Alekhnovich, Ben-Sasson, Razborov, Wigderson 2004;
                        \item Razborov 2015.
                    \end{itemize}
            \end{itemize}
        \pause
        \item Lower bound for Resolution systems of equations that encodes \textit{Sparse Weak Pigeonhole
            Principle} (\alert{$\NP$ vs. $\Ppoly$}).
            \begin{itemize}
                \item Open problem:
                    \begin{itemize}
                        \item Razborov 2004;
                        \item Urquhart 2008.
                    \end{itemize}
            \end{itemize}
    \end{itemize}

    \begin{enumerate}
        \item[] [\textcolor{blue}{S} 24] Random $(\log n)$-CNF are Hard for Cutting Planes. STOC 2024.
        \item[] [\textcolor{blue}{S} 20] (Semi)Algebraic proofs over $\pm 1$ variables. STOC 2020.
        \item[] [\textcolor{blue}{S} 22] Pseudorandom generators, resolution and
            heavy width. CCC 2022.
        \item[] [F. de Rezende, Nordstr{\"{o}}m, Risse, \textcolor{blue}{S} 20] Exponential resolution lower
            bounds for weak pigeonhole principle and perfect matching formulas over sparse graphs. CCC
            2020.
    \end{enumerate}
\end{frame}