\begin{frame}{Communication Protocols. $f\colon U \times V \to T$}
    \begin{center}
    	\input{pics/protocol.tex}    
    \end{center}

    \pause
    \pause
    \pause
	\pause

    \begin{itemize}
        \item Depth is the number of rounds (in the worst case).
        \item Size is the number of possible configurations.
    \end{itemize}
\end{frame}

\begin{frame}{$\Search_{\varphi}$ [Lov{\'{a}}sz, Naor, Newman, Wigderson et al. 94]}

    $\varphi(z) \coloneqq \bigwedge\limits_{i = 1}^{m} C_i$ is unsatisfiable CNF formula.
    \pause
    
    $\Search_{\varphi} \subseteq \{0, 1\}^n \times [m]$:
    \begin{itemize}
        \item $(\alpha, i) \in \Search_{\varphi} \Leftrightarrow C_{i}(\alpha) = 0.$
    \end{itemize}
    
    \pause
    \vspace{0.4cm}
    Communication version:
    \begin{itemize}
        \item partition of variables $Z = X \sqcup Y$ between Alice and Bob;
        \item $\varphi(x, y)$.
    \end{itemize}

\end{frame}

\begin{frame}{Why communication complexity?}

    \begin{itemize}
        \item Lower bounds for proofs of unsatisfiability of $\varphi$.
        \item Reduction of (monotone)Karchmer--Wigderson game $\Rightarrow$ circuit lower bounds.
        \item New techniques for comunication complexity.
    \end{itemize}
\end{frame}

\begin{frame}{$\Search_{\varphi}$ can be hard. Prior results}
    
\end{frame}


\begin{frame}{Random $\Delta$-CNF}

    \begin{minipage}{0.38\linewidth}
        \centering
        \input{pics/rand-graph.tex}
    \end{minipage}
    \begin{minipage}{0.58\linewidth}
        \begin{itemize}
            \item $m$ clauses;
            \item $n$ variables;
            \item $\Delta$ neighbours: $\binom{n}{\Delta}$ possibilities;
            \item negations (uniformly at random);
            \item $\mathfrak{D} \coloneqq \frac{m}{n}$ clause density.
        \end{itemize}
    \end{minipage}

    \pause
    \begin{itemize}
        \item $\mathfrak{D} > c_{\Delta} 2^{\Delta} \Rightarrow$ formula is unsat whp;
            \pause
        \item Fiege's conjecture: $\mathfrak{D} = \bigO{1} \Rightarrow$ no poly-time algorithm may
            ``prove'' unsatisfiability of random $\bigO{1}$-CNF.
            \begin{itemize}
                \item Non-approximability of many problems.
            \end{itemize}
    \end{itemize}

\end{frame}


\begin{frame}{Random CNF. Proir results}
    
\end{frame}