\begin{frame}{Tree-like communication protocols. $S \subseteq X \times Y \times \mathcal{T}$}

    Alice receives $x \in X$ and Bob receives $y \in Y$. A communication protocols corresponds to a tree:

    \begin{columns}[t]
		\begin{column}{0.6\textwidth}
            \begin{itemize}
                \item<2-> inner vertices are marked by players;
	            \item<3-> if current player sends a bit they move to next vertex;
    		    \item<8-> leaves are marked by answers.
	        \end{itemize}

            \vspace{0.5cm}
    		\onslide<9->{
                Reformulation: at each node players try to answer for the question: ``Which vertex will
                be next?''
            }
        \end{column}
        
		\begin{column}{0.3\textwidth}
            \input{pics/first_tree.tex}
		\end{column}
	\end{columns}

\end{frame}


\begin{frame}{Tree vs. Dag}

	\begin{columns}[t]
		\begin{column}{0.52\textwidth}
            \begin{center}
                Tree-like world.
                \only<1-2>{
                    ``Which vertex will be next?''
                }
                \only<3->{
                    \alert{``Are we in good vertex?''}
                }
                \vspace{0.2cm}
                \input{pics/tree_good.tex}
            \end{center}
        \end{column}

        \pause
		\begin{column}{0.48\textwidth}
            \begin{center}
                Dag-like world. ``Are we in good vertex?''
                \vspace{0.2cm}
                \input{pics/dag_good.tex}
            \end{center}
		\end{column}
	\end{columns}

    \pause
    \pause
    \vspace{0.4cm}
    Alice and Bob independently answer for this question.
\end{frame}

\begin{frame}{Dag protocols}
    \vspace{-0.8cm}
    \begin{columns}[t]
        \begin{column}{0.58\textwidth}
            \begin{itemize}
                \item $H$ is a graph with out degree $2$, $\forall h \in H, ~ C_h: X \times Y \to \{0,
                    1\}$;
                \item $C_{root} \equiv 1$;
                \item $a, b$ are children of $h$ $\Rightarrow$ $C_{h}^{-1}(1) \subseteq C_{a}^{-1}(1)
                    \cup C_{b}^{-1}(1)$;
                \item $h$ is a leaf $\Rightarrow$ $h$ is marked by common solution for $C_h^{-1}(1)$.
            \end{itemize}
        \end{column}

		\begin{column}{0.38\textwidth}
            \begin{center}
                \input{pics/dag.tex}
            \end{center}
		\end{column}
	\end{columns}

    \pause
    \begin{columns}[t]
		\begin{column}{0.48\textwidth}
            \begin{center}
                Rectangle (boolean) dag:
                \vspace{0.2cm}
                \input{pics/rectangle.tex}
            \end{center}
        \end{column}

		\begin{column}{0.48\textwidth}
            \begin{center}
                Triangle (real) dag:
                \vspace{0.2cm}
                \input{pics/triangle.tex}
            \end{center}
		\end{column}
	\end{columns}
\end{frame}


\begin{frame}{$\KWm$ relation (Karchmer, Wigderson 1990)}

    $f:\{0, 1\}^n \to \{0, 1\}$ is a monotone partial function
    
    \begin{itemize}
        \item Alice receives $x \in f^{-1}(1)$, Bob receives $y \in f^{-1}(0)$;
        \item goal is to find $i$ such that $x_i = 1 \land y_i = 0$.
    \end{itemize}

    \pause

    \begin{theorem}[Razborov 95; Pudl{\'{a}}k 10; S 17]
        Monotone boolean circuit for $f$ of size $S$ $\Leftrightarrow$ rectangle dag protocol of size $S$
        for the $\KWm_f$ relation.
    \end{theorem}

    \pause

    \begin{theorem}[Hrube{\v{s}} Pudl{\'{a}}k 17]
        Monotone real circuit for $f$ of size $S$ $\Leftrightarrow$ triangle dag protocol of size $S$
        for the $\KWm_f$ relation.
    \end{theorem}
\end{frame}


\begin{frame}{Canonical search problem $\Search_{\varphi}$ (Lov{\'{a}}sz et al. 1994)}
    
    $\varphi(x, y)$ is an unsatisfiable CNF formula:
    \begin{itemize}
        \item Alice receives a substitution to the variables $x$, Bob receives a substitution to the
            variables $y$;
        \item goal is to find a clause $C \in \varphi$ that is unsatisfied by this substitution.
    \end{itemize}

    \pause

    \begin{theorem}[Kraj{\'{\i}}{\v{c}}ek 95; S 17]
        $CC_{\log(n)}$ proof of $\varphi$ of size $S$ $\Rightarrow$ rectangle dag protocol for
        $\Search_{\varphi}$ of size $\poly(n) S$.
    \end{theorem}

    Resolution, $\CP^*$, $\dots$ are $CC_{\log(n)}$ proof systems.

    \pause
    
    \begin{theorem}[S 17]
        $\CP$ of $\varphi$ of size $S$ $\Rightarrow$ triangle dag protocol for $\Search_{\varphi}$ of
        size $S$.
    \end{theorem}
\end{frame}