план:

KW с доказательством.
Branching programs

Определение dag-like protocol.
KW с доказательством.

PLS games.
Эквивалентность.

Real games.
CP с доказательством.

Random CP


\begin{frame}{KW relation}
    \begin{definition}[Karchmer, Wigderson 1990]
        $\Bit$ relation for $U, V \subseteq \{0, 1\}^{n}$:
        \begin{itemize}
            \item Alice receive $u \in U$, Bob receive $v \in V$;
            \item goal is to find $i$ such that $u_i \neq v_i$.
        \end{itemize}
    	\pause    
        Monotone case ($\MBit$ relation):
        \begin{itemize}
            \item goal is to find $i$ such that $u_i = 1 \land v_i = 0$.
        \end{itemize}
    \end{definition}

    \pause

    \begin{theorem}[Karchmer, Wigderson 1990]
        There is a \onslide<4->{\alert{(monotone)}} boolean formula for function $f$ of size $S$ iff there is a communication
        protocol of size $S$ for $\Bit$ \onslide<4->{\alert{$(\MBit)$}} relation $U = f^{-1}(1), V = f^{-1}(0)$.
    \end{theorem}
\end{frame}


\begin{frame}{Protocols, trees, rectangles}

    \begin{theorem}[KW 1990, $\Leftarrow$] 
        There is a monotone boolean formula for function $f$ of size $S$ iff there is a communication protocol of size $S$
        for $\Bit$ $(\MBit)$ relation $U = f^{-1}(1), V = f^{-1}(0)$.
    \end{theorem}

    \pause
    Proof:

    
    \begin{enumerate}
        \item Communication protocol is a tree.
        \item Mark vertex $v$ by rectangle $R_v \subset U \times V$ (set of inputs that leads to vertex $v$).
        \item $f_v$ is a correct function on $R_v$.
    \end{enumerate}
\end{frame}


\begin{frame}{Intuition}


\end{frame}


\begin{frame}{Dag-like \only<9->{\alert{real}} communication game for relation $N: U \times V \to T$}
    Triple $(H, A, B)$, where $H$ is directed acyclic graph, $A: H \times U \to \only<-8>{\{0, 1\}}
    \only<9->{\alert{\mathbb{R}}}$~and $B: H \times V \to \only<-8>{\{0, 1\}} \only<9->{\alert{\mathbb{R}}}$.

    \pause
    $v \in H$ is valid for pair $(x, y)$ iff $A(v, x) > B(v, y)$.

    \pause

    \begin{columns}[t]
		\begin{column}{0.7\textwidth}
            \begin{itemize}
                \item<4-> Out-degree and all vertexes is at most $2$;
	            \item<5-> the leaves are marked by element of $T$;
    		    \item<6-> $\exists s \in H$ is valid for all pairs from $U \times V$;
		        \item<7-> if $h \in H$ is valid for $(x, y)$ and $h$ is not a leaf then at least one child of $h$ is valid for
	    	        $(x, y)$;
	    	    \item<8-> if $h \in H$ is valid for $(x, y)$, $h$ is a leaf and $h$ is marked by $t \in T$ then $t \in N(x, y)$.
	        \end{itemize}

    		\onslide<8->{The size of the game is the size of the graph $H$.}
        \end{column}
        
		\begin{column}{0.25\textwidth}
            \input{pics/prot_def.tex}
		\end{column}
	\end{columns}

\end{frame}

