\begin{frame}{KW relation (Karchmer, Wigderson 1990)}
    A relation $\Bit$ on sets $U, V \subseteq \{0, 1\}^{n}$:
    \begin{itemize}
        \item Alice receives $u \in U$, Bob receives $v \in V$;
        \item goal is to find $i$ such that $u_i \neq v_i$.
    \end{itemize}
    \pause
    Monotone case ($\MBit$ relation):
    \begin{itemize}
        \item goal is to find $i$ such that $u_i = 1 \land v_i = 0$.
    \end{itemize}

    \pause

    \begin{theorem}[Karchmer, Wigderson 1990]
        There is a \only<4->{\alert{(monotone)}} boolean formula for a function $f$ of the size $S$ iff there is a
        communication protocol of the size $S$ for the relation $\Bit$ \only<4->{\alert{$(\MBit)$}}, $U = f^{-1}(1), V =
        f^{-1}(0)$.
    \end{theorem}

    \pause
    \pause
    
    \begin{theorem}[Pitassi, G{\"{o}}{\"{o}}s, 2014]
        There is a monotone function $f$ such that any boolean formula that computes it has the size at least
        $2^{\frac{n}{\log(n)}}$. 
    \end{theorem}
\end{frame}

\begin{frame}{Canonical search problem $\Search_{\phi}$ (Beame et al. 2007)}
    
    $\phi(x, y)$ is an unsatisfiable CNF formula:
    \begin{itemize}
        \item Alice receives a substitution to the variables $x$, Bob receives a substitution to the variables $y$;
        \item goal is to find a clause $C \in \phi$ that is unsatisfied by this substitution.
    \end{itemize}

    \pause

    \begin{theorem}[Beame, Pitassi, Segerlind 2007. Informal]
        If there is a tree-like proof in proof system $\Pi$ ($\Pi$ from some \textit{huge class}) of size $S$ then there is a
        communication protocol for $\Search_{\phi}$ of depth $poly(\log(S))$.
    \end{theorem}

    \pause
    
    \begin{theorem}[Pitassi, G{\"{o}}{\"{o}}s, 2014]
        There is a formula $\phi$ such that the communication complexity of $\Search_{\phi}$ is at least $\frac{n}{\log(n)}$.
    \end{theorem}
\end{frame}

\begin{frame}{Generalization. Trivial way}

    Alice receives $u \in U$ and Bob receives $v \in V$. A communication protocols corresponds to a tree:

    \begin{columns}[t]
		\begin{column}{0.7\textwidth}
            \begin{itemize}
                \item<2-> inner vertices are marked by players;
	            \item<3-> if current player sends a bit they move to next vertex;
    		    \item<8-> leaves are marked by answers.
	        \end{itemize}

    		\onslide<9->{The size of the game is the size of the graph $H$.}

            \onslide<10->{Can we merge some vertex?}

			\onslide<13->{
                \begin{block}{Remark}
                    It is too powerful model. There are short protocols for $\Bit$, $\MBit$ and $\Search_{\phi}$.
                \end{block}
            }
        \end{column}
        
		\begin{column}{0.25\textwidth}
            \input{pics/classic.tex}
		\end{column}
	\end{columns}

\end{frame}

\begin{frame}{Generalization. Rectangles}

    Alice receives $u \in U$ and Bob receives $v \in V$.

    \begin{columns}[t]
		\begin{column}{0.6\textwidth}
            \begin{itemize}
                \item<2-> Mark all vertices $h$ of the tree by rectangles $R_h = U_h \times V_h \subseteq U \times V$;
	            \item<4-> $(u, v) \in R_h$ iff $h$ is on path from root to leaf for instance $(u, v)$;
    		    \item<5-> payment for merge $h$ and $h'$: cover by rectangle $R_{new}$.
	        \end{itemize}
            
            \onslide<6->{
                \begin{center}
                	\input{pics/covers.tex}    
                \end{center}
            }
        \end{column}
        
		\begin{column}{0.3\textwidth}
            \onslide<3->{\input{pics/classic_2.tex}}
		\end{column}
	\end{columns}
\end{frame}