\begin{frame}

    \begin{center}
        \Huge Part V: Barriers
    \end{center}
    
\end{frame}

\begin{frame}{Problems with lower bounds}

    \begin{enumerate}
        \item Lack of candidates that should be hard.
        \item Lack of technique.
    \end{enumerate}

    \pause
    What so hard to find candidate?
    \pause
    \begin{enumerate}
        \item Candidate is a collection of \alert{unsat} formulas.
        \item There is a human proof of unsatisfiability.
        \item And this proof maybe realized in some proof system.
    \end{enumerate}
\end{frame}

\begin{frame}{Random $\Delta$-CNF}

    \begin{minipage}{0.38\linewidth}
        \centering
        \input{pics/rand-graph.tex}
    \end{minipage}
    \begin{minipage}{0.58\linewidth}
        \begin{itemize}
            \item $m$ clauses;
            \item $n$ variables;
            \item $\Delta$ neighbours: $\binom{n}{\Delta}$ possibilities;
            \item negations (uniformly at random);
            \item $\mathfrak{D} \coloneqq \frac{m}{n}$ clause density.
        \end{itemize}
    \end{minipage}

    \pause
    \begin{itemize}
        \item $\mathfrak{D} > c_{\Delta} 2^{\Delta} \Rightarrow$ formula is unsat whp;
            \pause
        \item Fiege's conjecture: $\mathfrak{D} = \bigO{1} \Rightarrow$ no poly-time algorithm may
            ``prove'' unsatisfiability of random $\bigO{1}$-CNF.
            \begin{itemize}
                \item Non-approximability of many problems.
            \end{itemize}
    \end{itemize}

\end{frame}

\begin{frame}{Lower bounds in proof complexity}

    \input{pics/hier-rand.tex}
\end{frame}

\begin{frame}{Restriction Technique}

    \begin{lemma}
        Any CNF representation of $\Parity\colon \{0, 1\}^n \to \{0, 1\}$ has size at least
        $2^{\bigO{n}}$.
    \end{lemma}

    \pause
    \begin{enumerate}
        \item Assume that $\varphi \coloneqq \bigwedge C_i$ of small size computes $\Parity$.
            \pause
        \item Assign $\varepsilon n$ variables uniformly at random.
            \pause
        \item Only clauses with few variables can survive. But $\Parity$ is still $\Parity$.
            \pause
        \item It remains to show that any CNF representation of $\Parity$ require clauses with large
            number of variables.
    \end{enumerate}

    \pause
    \vspace{0.5cm}
    \begin{itemize}
        \item Same ideas works for: resolution, $\CP$, $\NS$, $\SOS$, etc.
        \item For all proof systems such that the size of proof is easy to shrink by
            restriction.  
    \end{itemize}

\end{frame}

\begin{frame}{Hierarchy}

    \input{pics/hier-restriction.tex}
    
\end{frame}