\begin{frame}{$\OBDD(\land, \weakening)$-proofs}
    \begin{itemize}
        \item $\phi = C_1 \land C_2\land \dots \land C_t$ is unsatisfiable CNF.
        \item Choose order $\pi$; every $C_i$ is represented as $\pOBDD$.
        \item Join (conjunction) rule: $\frac{D_1^{\pi} ~~~ D_2^{\pi}} {(D_1\land D_2)^{\pi}}$.
        \item Weakening rule: $\frac{D^{\pi}}{D_1^{\pi}}$ if $D \models D_1$.
        \item Proof of unsatisfiability of $\phi$: derivation a constant false $\OBDD$.
        \pause
        \item{} [Atserias, Kolaitis, Vardi, 2004] $\OBDD(\land, \weakening)$ simulates $\CP^*$
            \pause $\implies \PHP^{n + 1}_n$ has proofs of poly size.
        \pause
        \item Unsatisfiable linear systems over $\mathbb{F}_2$ have short proofs.
        \pause
        \item{} [Segerlind, 2007] $2^{n^{\Omega(1)}}$-lower bound for tree-like $\OBDD(\land,
            \weakening)$-proofs.
        \item{} [Kraj{\'{\i}}{\v{c}}ek, 2008] $2^{n^{\Omega(1)}}$-lower bound for dag-like $\OBDD(\land,
            \weakening)$-proofs.
    \end{itemize}
\end{frame}

\begin{frame}{Kraj{\'{\i}}{\v{c}}ek's monotone interpolation}

    \fbox{Proof of $\CliCol$ in semantic calculus} $\mapsto$
    \fbox{mon. circuit, separating $(k + 1)$-cliques from $k$-col. graphs}.

    \pause

    \begin{theorem}[Kraj{\'{\i}}{\v{c}}ek, 1998]
        There is a partition of variables of $\CliCol_n$ such that every semantic proof of $\CliCol_n$
        either has constraint with $\CC$ at least $t$ or has size at least $2^{n^{\delta} - t}$. 
    \end{theorem}

    \pause

    Corollaries[Kraj{\'{\i}}{\v{c}}ek, 2008]:
    \begin{itemize}
        \item There exists an order $\pi$ such that every $\pOBDD(\land,
            weakening)$ has size at least $2^{\frac{1}{2} n^\delta}$.
    \end{itemize}

    \pause
    Hard formula for all orders? \pause $\Phi(x) \mapsto \Psi(x, y)$.
    
    \begin{itemize}
        \item $\forall$ orders $\pi$ on $x$ there is a substitution $y_{\pi}$ such that $\Psi(x,
            y_{\pi})$ is isomorphic to $\Phi(x)$.
        \item $\Psi(x, y)$ is hard for all orders if $\Phi(x)$ is hard for at least one.
    \end{itemize}
\end{frame}

\begin{frame}{$\OBDD(\land)$-proofs}
    \begin{itemize}
        \item{} [Groote, Zantema, 2003; Tveretina et al., 2009] $OBDD(\land)$-proof system is
            not simulates resolution;
        \item{} [Tveretina et al., 2009] $\PHP^{n + 1}_n$ requires $OBDD(\land)$-proofs of size
            $2^{\Omega(n)}$;
        \item{} [Friedman, Xu, 2013] random $3$-CNFs are hard for $OBDD(\land)$-proofs in two particular
            cases:
            \begin{itemize}
                \item with a fixed order of the variables;
                \item with fixed orders of application of rules.
            \end{itemize}
    \end{itemize}    
\end{frame}


\begin{frame}{Reordering rule}
    $\OBDD(\land, \reordering)$:
    \begin{itemize}
    	\item reordering rule: $\frac{D_1^{\pi_1}}{D_2^{\pi_2}}$ where $D_1^{\pi_1} \equiv D_2^{\pi_2}$;
        \item join (conjunction) rule: $\frac{D_1^{\pi} ~~~~ D_2^{\pi}}{(D_1 \land D_2)^{\pi}}$.
    \end{itemize}

    \pause
	Our results:
    \pause
    \begin{itemize}
        \item $\OBDD(\land, \reordering)$ is strictly stronger than $\OBDD(\land)$;
        \pause
        \item lower bound $2^{\Omega(n)}$ for $\PHP^{n + 1}_n$ in $\OBDD(\land, \reordering)$;
        \item lower bound $2^{\Omega(n)}$ for Tseitin formulas in $\OBDD(\land, \reordering)$;
        \pause
        \item $\OBDD(\land, \weakening)$ has short proofs of $\CliCol$ in some order;
        \item $\OBDD(\land, \weakening, \reordering)$ is strictly stronger than $\OBDD(\land,
            \weakening)$.
    \end{itemize}

    \pause
    {\color{blue} Open question.} Prove superpolynomial lower bound for $\OBDD(\land, \weakening,
    \reordering)$.
\end{frame}