
\begin{frame}
    \frametitle{Деревья лиенйных расщеплений (LST)}
	Расщепления по линейным формам над полем $\mathbb{F}_2$
    \begin{columns}
        \begin{column}{3cm}
            Вырожденый лист
            \input{pics/linear/case_degenerate.tex}
        \end{column}
        \begin{column}{3cm}
            Выполняющий набор
            \input{pics/linear/case_solution.tex}
        \end{column}
        \begin{column}{3cm}
            Противоречие с клозом
            \input{pics/linear/case_contradiction.tex}
        \end{column}
    \end{columns}
    
	$\Phi$ опровергает $(x_1 \lor x_2 \dots \lor x_k)$ $\Leftrightarrow$ $\Phi \land (x_i = 1)$ невыполнима $\forall i$.
\end{frame}

\begin{frame}
    \frametitle{Splitting trees}
    $(\lnot x \lor y) \land (x \lor \lnot y) \land (\lnot y \lor z) \land
    	(y \lor \lnot z) \land (x \lor z) \land (\lnot x \lor \lnot z)$ 
	\only<1>{\input{pics/linear/DPLL_tree_new.tex}}
	\only<2>{\input{pics/linear/p_DPLL_tree_new.tex}}
\end{frame}


\begin{frame}
    \frametitle{Алгоритм Сето и Тамаки}

	\begin{itemize}
		\item{} [Seto, Tamaki, 2011] Алгоритм для Formula-SAT над полным бинарным базисом. Для формул размера $cn$ алгоритм
		    работает $2^{(1 - \mu_c)n}$ шагов, где $\mu_c$~--- константа.
        \pause
		\item Алгоритм использует расщепление по линейным комбинациям.
	\end{itemize}    
\end{frame}


\begin{frame}
    \frametitle{Верхние оценки}

    \begin{itemize}
		\item Линейные системы над $\mathbb{F}_2$:
			\begin{itemize}
				\item трудны для резолюций;
				\item просты для LST.
			\end{itemize}
        \pause
		\item Perfect matching principle для графов с нечетным числом вершин:
		    \begin{itemize}
        		\item трудны для резолюций [Разборов, 2003];
				\item просты для LST.
			\end{itemize}
        \pause
		\item Игры с фишками.
			\begin{itemize}
				\item Пусть $\phi$ формула в КНФ обощначим за $\phi^{\oplus}$ КНФ формулу, полученную из $\phi$ путем подстановки
		            $x_1 \oplus x_2$ для каждой переменной $x$. 
				\item{} [Urquhart, 2011] Размер древесного вывода в резолюциях $\phi^{\oplus}$ не менее $2^{d(\phi)}$, где
		            $d(\phi)$ минимальная глубина резолюционного вывода для  $\phi$.
				\item{} [Urquhart, 2011] Для игры с фишками $Peb(G_n)$ выполнено: $d(Peb(G_n)) = \Omega(n / \log(n))$ и $Peb(G_n)$
		            имеет $O(n)$ древесный резолюционный вывод.
				\item Древесный резолюционный вывод для $Peb^\oplus(G_n)$ не менее $2^{n / \log n}$, но $Peb^\oplus(G_n)$ имеет
		            LST размера $O(n)$. 
			\end{itemize}
	\end{itemize}
\end{frame}




\begin{frame}
    \frametitle{Linear systems}

    \begin{columns}
		\begin{column}{1cm}
			Unsatisfiable system:

			$\left\{ \begin{aligned}
				f_1 = \alpha_1 \\
				f_2 = \alpha_2 \\
				\dots\\
				f_m = \alpha_m
			\end{aligned}\right.$
		\end{column}


		\begin{column}{9cm}
			\input{pics/linear/system.tex}
		\end{column}
	\end{columns}

	$f_2 = x_1 + \dots + x_k$
\end{frame}

\begin{frame}
    \frametitle{Lower bound for 2-fold Tseitin formulas}

    \begin{itemize}
		\item For unsatisfiable $\phi$ a search problem $Search_\phi$: find a
		    falsified clause given a variable assignment.
        \pause 
		\item We prove that it is possible to transform a splitting tree $T$ into a
		    randomized communication protocol for the problem $Search_\phi$ of depth
	        $O(\log |T| \log\log |T|)$ if some variables are known by Alice and other
	        variables are known by Bob.
        \pause
		\item Use a lower bound on the randomized communication complexity of the
		    problem $Search_{TS^2_{G,c}}$ for a 2-fold Tseitin formula $TS^2_{G,c}$
            that follows from [Kalyanasundaram, Schintger 1992] and
            [Beame, Pitassi, Segerlind, 2007].
	\end{itemize}
	\pause
    \begin{theorem}
        In time polynomial in $n$ one may construct a graph $G(V, E)$ on $n$ vertices
        with maximal degree bounded by a constant and a function $c: V \to
        \mathbb{F}_2$ such that the size of any linear splitting tree of
        $TS^2_{(G,c)}$ is at least $\Omega\left(2^{n^{1 / 3} / \log^3(n)} \right)$.
    \end{theorem}
\end{frame}



\begin{frame}
    \frametitle{Res-Lin}

    \begin{itemize}
		\item Literal: $L = x_{1} + x_{2} + \dots + x_{k} = \alpha$,
    		$\lnot L = x_{1} + x_{2} + \dots + x_{k} = \alpha + 1$
		\item Linear clause: $\bigvee_i x_{i, 1} + x_{i, 2} + \dots + x_{i, k_i} =
		    \alpha_i$ or $\lnot \bigwedge x_{i, 1} + x_{i, 2} + \dots + x_{i, k_i} =
            1 + \alpha_i$.
        \pause
		\item Res-Lin:
			\begin{itemize}
				\item Resolution rule: $\frac{(f = 0) \lor D, (f = 1) \lor D'}
            		{D \lor D'}$ 
				\item Weakening rule: $\frac{C}{C'}$ if $C$ semantically implies $C'$
			\end{itemize}
        \pause
		\item \mycolor{blue}{Tree-like} Res-Lin is equivalent to LST.
	\end{itemize}
	\scalebox{0.8}{\input{pics/linear/DPLL_to_proof.tex}}
\end{frame}



\begin{frame}
    \frametitle{Res-Lin vs Sem-Lin}

    \begin{itemize}
		\item Sem-Lin:
			\begin{itemize}
				\item Semantic rule: $\frac{C_1, C_2}{C'}$ if $C_1 \land C_2$
		            semantically implies $C'$
				\item Weakening rule: $\frac{C}{C'}$ if $C$ semantically implies $C'$
			\end{itemize}
	\end{itemize}

	\pause
    \begin{theorem}
        Res-Lin p-simulates Sem-lin.
    \end{theorem}

	\pause
    \begin{block}{Example}
        How to get $(x + y = 0)$ from $(x = 0)$ and $(y = 0)$ in Res-Lin?
    \end{block}


    \begin{columns}
		\begin{column}{5cm}
            \begin{itemize}
            	\item $\frac{(x = 0)}{(x + y = 0) \lor (y = 1)}$
            \end{itemize}
		\end{column}
		\begin{column}{5cm}
            \begin{itemize}
            	\item $\frac{(x + y = 0) \lor (y = 1),(y = 0)}{(x + y = 0)}$
            \end{itemize}
		\end{column}
	\end{columns}
%	\begin{itemize}
%		\item $\frac{(x = 0)}{(x + y = 0) \lor (y = 1)}$
%		\item $\frac{(x + y = 0) \lor (y = 1),(y = 0)}{(x + y = 0)}$.
%	\end{itemize}

	\pause
    \begin{theorem}
        Res-Lin is implication complete.
    \end{theorem}

	\begin{itemize}
        \pause
		\item The weakening rule may be simulated by a polynomial number of pure
	        syntactic rules.
%		 \begin{itemize}
%			\item The simplification rule: $\frac{D \lor (0 = 1)}{D}$; 
%			\item The syntactic weakening rule: $\frac{D}{D \lor (f = \alpha)}$;
%			\item The addition rule: $\frac{D \lor (f_1 = \alpha_1) \lor
%		        (f_2 = \alpha_2)}{D \lor (f_1 = \alpha_1) \lor
%                (f_1 + f_2 = \alpha_1 + \alpha_2 + 1)}$ 
%		\end{itemize}
	\end{itemize}
\end{frame}



\begin{frame}
    \frametitle{R(lin)}

    R(lin) [Raz, Tsameret, 2007] operates with disjunction of linear equalities with
    \mycolor{blue}{integer} coefficients.
    
	\begin{itemize}
		\item Resolution rule: $\frac{A \lor (F_1 = a_1), B \lor (F_2 = a_2)}
    		{A \lor B \lor (F_1 \pm F_2 = a_1 \pm a_2)}$
		\item Weakening rule: $\frac{A}{A \lor (F = a)}$
		\item Simplification rule: $\frac{B \lor (0 = c)}{B}$, where $c \neq 0$. 
	\end{itemize}

	\pause
    \begin{theorem}
    	R(lin) p-similates Res-Lin.    
    \end{theorem}
    
	\medskip

	\pause
	\begin{columns}
		\begin{column}{5cm}
			$x_1 + x_2 + \dots + x_n \equiv 0 \bmod 2$:
			$\left[\begin{aligned}
            	x_1 + &\dots + x_n = 0\\
                x_1 + &\dots + x_n = 2\\
                &\dots \\
                x_1 + &\dots + x_n = 2 \lceil n / 2 \rceil
            \end{aligned}\right.$ 
		\end{column}
		\begin{column}{5cm}
			$x_1 + x_2 + \dots + x_n \equiv 1 \bmod 2$:
			$\left[\begin{aligned}
                x_1 + &\dots + x_n = 1\\
                x_1 + &\dots + x_n = 3\\
                &\dots \\
                x_1 + &\dots + x_n = 2 \lceil (n - 1) / 2 \rceil + 1
            \end{aligned}\right.$
		\end{column}
	\end{columns}
\end{frame}


\begin{frame}
    \frametitle{Futher research}

    \begin{itemize}
		\item Prove lower bound for dag-like Res-Lin.
		\item What is tree-like Res-Lin complexity of the Perfect Matching Principle
		    for $K_{n - 2, n}$? 
		\item Does tree-like Res-Lin p-simulate dag-like Resolution?
		\item Does PCR p-simulate Res-Lin?
		\item Prove lower bound for splitting by linear combinations on
		    \mycolor{blue}{satisfiable} formulas.
	\end{itemize}
\end{frame}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
