\begin{frame}{Craig's interpolation theorem, 1957}

    Let $U, V \in \{0, 1\}^n$ are disjoint $\NP$ sets:
    \begin{itemize}
        \item the formula $\One(x, q)$ encodes the fact that $x \in U$;
        \item the formula $\Zero(x, r)$ encodes the fact that $x \in V$;
        \item $\One(x, q) \land \Zero(x, r)$ is the unsatisfiable formula.
            
    \end{itemize}

    \vspace{0.2cm}
    \pause
    Example: $U$ is a set of graphs on $n$ vertices with a clique of size $k$, $V$ is a set graphs on $n$
    vertices that can be colored into $k - 1$ colors.

    \pause
    \begin{definition}
	    $C: \{0, 1\}^n \to \{0, 1\}$ is a separator for $U, V$ iff:
        \begin{itemize}
            \item $C(U) = 1$;
            \item $C(V) = 0$.
        \end{itemize}        
    \end{definition}

    \pause
	What can we say about the complexity of $C$?

\end{frame}


\begin{frame}{Monotone interpolation}

    \begin{block}{Crucial idea, Kraj{\'{\i}}{\v{c}}ek}
        If there is a short proof of $\One(x, q) \land \Zero(x, r)$ then separator $C$ has a small
        \alert{monotone} {\color{blue} circuit} complexity (if it exists). 
    \end{block}

    \begin{theorem}[Razborov 85, Alon-Boppana 87]
        The size of any monotone separator for $\CliqueColoring$ is at least $2^{n^{\frac{1}{4}}}$.
    \end{theorem}

    \pause
    Reasonable encoding:
    \begin{itemize}
        \item clauses contain at most one variable from $x$;
        \item $x$ occurs in $\One$ only with positive signs and in $\Zero$ only with negative signs.
    \end{itemize}
\end{frame}

\begin{frame}{Monotone interpolation property}

    Proof system $\Pi$ has a monotone interpolation property:
    
    any proof of reasonable encoding of $\One(x, q) \land \Zero(x, r)$ of size $S$ $\Rightarrow$ monotone circuit
    of size $\poly(S)$ for separator $C$.

    \pause
    \begin{block}{Positive results}
        \begin{itemize}
            \item {[Kraj{\'{\i}}{\v{c}}ek, 95]} Resolution (and huge class of semantic proof systems) has
                the monotone interpolation property.
            \item {[Pudl{\'{a}}k, 97]} Cutting Planes has the monotone interpolation property.
        \end{itemize}
    \end{block}

    \pause
    \begin{block}{Negative results}
        \begin{itemize}
            \item {[Bonet, Pitassi, Raz 00, Bonet et al. 04]} Frege system does not have the monotone
                interpolation property.
            \item {[Atserias, Bonet, Esteban 02]} Res(2) system does not have the monotone interpolation 
                property.
        \end{itemize}
    \end{block}
    
\end{frame}

\begin{frame}{Negative results?}

    \begin{theorem}[Atserias, Bonet, Esteban 02]
        There is a $\Res(2)$ proof of $\CliqueColoring$ of polynomial size.
    \end{theorem}

    \pause
    $\OBDD$ proof system is a semantic proof system that operates with $\OBDD$s.

    \begin{itemize}
        \item {[Kraj{\'{\i}}{\v{c}}ek 08]} If there is a short proof of {\color{blue} modified}
            $\CliqueColoring$ in $\OBDD$ proof system then there is a small separator for
            $\CliqueColoring$.
        \item {[Buss, Itsykson, Knop, S 17]} There is a proof of $\CliqueColoring$ of polynomial size in
            the $\OBDD$ proof system.
    \end{itemize}
\end{frame}

\input{parts/plan.tex}